---
title: "8105 HW6"
output: github_document
date: '2022-12-3'
---

```{r}
# load libraries
library(tidyverse)
library(rvest)
library(httr)
library(purrr)
library(patchwork)
library(viridis)
library(modelr)
library(mgcv)
```

# Problem 2
```{r}
# import the data 
url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide_df = read_csv(url) %>% 
  janitor::clean_names()
```

```{r}
# tidy it according to the requirements
# resolved = 1, unresolved = 0
homicide_df = 
  homicide_df %>% 
  mutate(
    city_state = paste(city, state, sep = ","),
    disposition = ifelse(disposition == "Closed by arrest", 1, 0),
    victim_age = as.numeric(victim_age),
    victim_race = fct(victim_race)
  ) %>% 
  filter(city_state != "Dallas,TX" & city_state != "Phoenix,AZ" & city_state != "Kansas City,MO" & city_state != "Tulsa,AL") %>% 
  filter(victim_race == "White" | victim_race == "Black")
```

```{r}
homicide_summary_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  select(city_state, disposition, victim_age, victim_sex, victim_race)
```

```{r}
# Baltimore,MD
Baltimore_df = 
  homicide_summary_df %>% 
  filter(city_state == "Baltimore,MD") 
  
 
test_Baltimore = 
  glm(disposition ~ victim_age + victim_sex + victim_race, data = Baltimore_df, family = binomial()) %>%
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower_bound = exp(estimate - 1.96 * std.error),
    CI_upper_bound = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, estimate, OR, CI_lower_bound, CI_upper_bound) %>% 
  knitr::kable(digits = 4)
test_Baltimore

```

```{r}
# all other cities' data
cities_stats = 
  homicide_summary_df %>% 
  nest(reg_data = -city_state) %>% 
  mutate(
    reg_line = map(.x = reg_data, ~glm(disposition ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
    reg_line = map(reg_line, broom::tidy)
  ) %>% 
  select(-reg_data) %>% 
  unnest(reg_line) %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    OR = exp(estimate),
    CI_lower_bound = exp(estimate - 1.96 * std.error),
    CI_upper_bound = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, OR, CI_lower_bound, CI_upper_bound)

# making a plot
OR_plot =
  cities_stats %>% 
  ggplot(aes(x = fct_reorder(city_state, OR), y = OR)) + geom_point() + geom_errorbar(aes(ymin = CI_lower_bound, ymax = CI_upper_bound)) +
  labs(title = "OR for solving homicides comparing male to female", x = "City/State", y = "OR") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.9, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5)) 

OR_plot
```
comment of the OR plot:
New York has the lowest estimated OR and Albuquerque has the highest estimated OR and it also has the widest confidence interval. Some cities like San Bemardino has lower OR than some other cities but it has wider associated confidence interval.

# Problem 3
```{r}
# data manipulation, check for any missing values
birth_df =
  read_csv("birthweight.csv") %>% 
  janitor::clean_names() %>% 
  select(bwt, everything()) %>% 
  drop_na()
```
comment: The size of the birthweight dataset doesn't change before and after dropping the NAs, so there is no missing value in the dataset.

```{r}
# convert numeric to factor where appropriate
birth_df %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace),
    parity = as.factor(parity),
    pnumlbw = as.factor(pnumlbw),
    pnumsga = as.factor(pnumsga)
  )
```

```{r}
# model building
# 1st step: put all variables into the model to check the possible coefficients
model_check = 
  lm(bwt ~ ., data = birth_df) %>% 
  broom::tidy()

model_check
```
comment: variables "pnumlbw", "pnumsga", "wtgain" have no estimate, so we rule them out from the original model and build another model without them.

```{r}
# find the "best" model 
model_check_update =
  lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + ppbmi + ppwt + smoken, data = birth_df)

model_check_update %>% 
  broom::tidy()
```

```{r}
# add predictions and residuals to the model_check_update
birth_df %>% 
  add_residuals(model_check_update) %>% 
  add_predictions(model_check_update) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.2) +
  geom_line(aes(y = 0), color = "red") +
  labs(
    title = "Fitted Values vs Residuals Based on the Built Model",
    x = "Fitted Values",
    y = "Residuals"
    ) +
  theme(plot.title = element_text(hjust = 0.5))
```
comment: the residuals are basically symmetric around y=0, and centered around the "y=0" line which makes sense.
  
```{r}
# first comparison model
model1 = lm(bwt ~ blength + gaweeks, data = birth_df) %>% 
  broom::tidy()
model1
```

```{r}
# second comparison model
model2 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birth_df) %>% 
  broom::tidy()
model2
```

```{r}
# comparison models
compare_models = 
  crossv_mc(birth_df,100) %>% 
  mutate(
    train = map(train,as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    model1_train = map(train, ~lm(bwt ~ blength + gaweeks, data = birth_df)),
    model2_train = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birth_df)),
    model_check_update_train = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + ppbmi + ppwt + smoken, data = birth_df))
  ) %>% 
  mutate(
    rmse_model1 = map2_dbl(model1_train, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2_train,  test, ~rmse(model = .x, data = .y)),
    rmse_model_check_update = map2_dbl(model_check_update_train, test, ~rmse(model = .x, data = .y)),
  )
```
modeling process description:

```{r}
# draw a violin plot to compare three models (some code from lecture)
compare_models %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(
    model = fct_inorder(model)
  ) %>% 
  ggplot(aes(x = model, y = rmse,color = model)) + 
  geom_violin()+
  labs(
    x = "Three Different Models",
    y = "rmse",
    title = "Comparison of Three Models"
  )+
  theme(plot.title = element_text(hjust = .5))
```
comment:









